### 2021-04-03 Chapter-3/Chapter-3.tex
update

>>>>

\begin{table*}[]
  \centering\small\footnotesize
  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
      Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
      The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
  }\label{table:over_result}
  \newlength{\x}
  \newlength{\y}
  \settowidth{\x}{~~}
  \settowidth{\y}{m}
  \addtolength{\x}{-1\y}
  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
%    \resizebox{1.9\columnwidth}{!}{
  \begin{threeparttable}
  \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
      \hline
      \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
                         & \textbf{\# Instructions}    & \textbf{SE} & \textbf{MC}                                                    \\\hline
                                               &                        &                     &                      &              & ms                     \\
      AES\tnote{1}               & 68                     & 0                   & 68                   & 39,855        & 512     & 1,052         \\
      AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520    & 1,057         \\
      AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231    & 9,199        \\
      AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36      & 1,924         \\
      AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35      & 1,961        \\
      AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36     & 2,161        \\
      AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      & 1,631        \\
      DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58      & 162          \\
      DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      & 162           \\
      DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    & 4,677         \\
      DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166    & 6,509        \\
      DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165    & 5,975        \\
      DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182    & 5,292        \\
      DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     & 5,152      \\
                         &                        &                     &                      &                  & seconds                  \\
      Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2     & 0             \\  
      Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15    & 0             \\
      Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    & 0             \\
      Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271   & 0            \\
      ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48   &   31       \\ 
      ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102   & 1639          \\   
      ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     & 62           \\   
      ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100     & 58            \\   
      ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76      & 42                  \\  
      ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121     & 0                  \\  
      ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102     & 59        \\

                         &                        &                     &                      &                 & minutes            \\
      RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39     & 41           \\
      RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44     & 251           \\
      RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23      & 428           \\
      RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29     & 436          \\
      RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40     & 714          \\
      RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      & 490         \\
      RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8      & 53          \\
      RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5      & 780         \\
      RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
      RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
      RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    & 6560       \\

      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  & 10,232m     \\\hline
  \end{tabular}
\end{threeparttable}
\begin{tablenotes}
  \scriptsize

  \item[1] mbedTLS\,2.5  ~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
  \item[4] OpenSSL\,0.9.7  ~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k \\
  \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
  \item[10] Libgcrypt\,1.6.1 \item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
\end{tablenotes}
\end{table*}
